HCI Project Proposal and Preliminary Literature Review

### 2015-10-07 sigchi-latex-proceedings 2/proceedings.tex
REMOVED LICENSE & KEYWORDS
Add small changes to formatting
Hasn’t been converted to PDF

\keywords{CSC428}

@@

\section{Literature Review}
The research on application switchers in smartphones is quite sparse. However, there has been research conducted on the costs of interruption when application switching to a user's workflow, as well as designing more efficient application switching interfaces for web and desktops. The results of this research help inform the design of this study.

@@

Nagata [4] examined the impact of distractions on performing a main task as well as handling a secondary task on mobile and desktop devices. The study measured the total time taken and the accuracy of completing both tasks, as well as the time to transition between tasks. One of the take-aways from this was the impact of switching apps on a mobile device on distraction time. While this device was from 2001, and there have been marked improvements in handheld devices, slow transition times between activities negatively impacted all the metrics. Determining an effective method to manage apps will allow users to use their devices and apps better overall.

@@

Leiva et al. [4] explored the cognitive costs of intended and unintended app switching and found that performing an app switch can increase completion time of a task by a factor of four. The authors propose several methods to reduce app switching cognitive overhead, such as replaying N milliseconds of previous UI interactions, however they do not examine the app switching mechanism itself. We plan to investigate incorporating some motion into the app switching interface itself to help users more effectively recognize the target app and regain their task state. The paper estimated app switching events to be at most 10% of daily application usage, thereby underscoring the necessity for having an effective app switching interface.

@@

>>>>

@@

\section{Literature Review}
The research on application switchers in smartphones is quite sparse. However, there has been research conducted on designing more effective application switching interfaces for web and desktops. The results of this research help inform the design of this study.

@@

Nagata [4] examined the impact of distractions on performing a main task as well as handling a secondary task on mobile and desktop devices. The study measured the total time taken and the accuracy of completing both tasks, as well as the time to transition between tasks. One of the take-aways from this was the impact of switching apps on a mobile device on distraction time. While this study was from 2001, and there have been marked improvements in handheld devices, slow transition times between activities negatively impacted all the metrics. Determining an effective method to manage apps will allow users to use their devices better overall.

@@

@@

Leiva et al. [4] explored the cognitive costs of intended and unintended app switching and found that performing an app switch can increase completion time of a task by a factor of four. The authors propose several methods to reduce app switching cognitive overhead, such as replaying N milliseconds of previous UI interactions, however they do not examine the app switching mechanism itself. We plan to investigate incorporating some motion into the app switching interface itself to help users more effectively recognize the target app and regain their task state. The paper estimated app switching events to be at most 10\% of daily application usage, thereby underscoring the necessity for having an effective app switching interface.
